---
title: "Combine Plots"
author: "Matthias Westhues"
date: "April 12, 2017"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman")
pacman::p_load_gh("tidyverse/dplyr")
pacman::p_load("ggplot2", "cowplot", "grid", "gridBase", "purrr")
```


## ggplot2 facets
We want to plot the same type (e.g. a scatterplot) but for multiple facets of
the data. 
This can easily be done using either `facet_wrap` or `facet_grid` in `ggplot2`.
```{r ggplot2}
data(mtcars)
car_scatter <- mtcars %>% 
  ggplot(aes(x = disp, y = mpg)) +
  geom_point() +
  facet_grid(. ~ cyl, scales = "free") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.spacing.x = unit(2, "lines")
  )
car_scatter
```

## ggplot2 of different type
We are interested in looking different aspects of the data, using various plot
types, but displaying them all in a single plot.
The `cowplot` package can be used for this when all plots are created using
the `ggplot2` package.
```{r cowplot}
# Create a new regression plot.
car_reg <- mtcars %>% 
  ggplot(aes(x = disp, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_grey(base_size = 8)

# Create a new bar plot.
convert_to_factor <- compose(as.character, as.factor)
car_boxplots <- mtcars %>% 
  ggplot(aes(x = cyl %>% convert_to_factor(), y = hp)) +
  geom_boxplot() +
  theme_grey(base_size = 8) +
  xlab("# Cylinders") +
  ylab("Horsepower")

# Combine the previous plots.
bottom_row <- plot_grid(
  car_reg, car_boxplots,
  labels = c("B", "C"),
  align = "h",
  rel_widths = c(1, 1)
)

plot_grid(
  car_scatter,
  bottom_row,
  labels = c("A", ""),
  ncol = 1,
  rel_heights = c(2, 1)
)

```



