---
title: "File transfer using 'rsync'"
---

1.   The general layout of any `rsync` command is as follows:
```{r, tidy = FALSE, eval = FALSE}
rsync [OPTION] SRC DEST
```
where `SRC` is the source to copy from and `DEST` is the receiving location of 
the files sent from `SRC`.

2.   Check what will happen first
Always make sure to conduct a dry run before actually running `rsync` by appending the command with the `-n`
(i.e. `--dry-run``) flag:
```{r, tidy = FALSE, eval = FALSE}
rsync -avv --dry-run SRC DEST
```

3.   Copy only existing files and only if newer than target
```{r, tidy = FALSE, eval = FALSE}
rsync -avv --dry-run --update --existing src/ dest
```
[source](http://unix.stackexchange.com/a/117193)

4.   Copy only files from `src` itself, but from none of its child directories
```{r, tidy = FALSE, eval = FALSE}
rsync -avv --dry-run -f '- /*/' src/ dest
```
[source](http://superuser.com/a/436079)

5.   Compress files when using rsync
```{r, tidy = FALSE, eval = FALSE}
rsync -z src/ dest
```

6.   Using rsync over a Network
```{r, tidy = FALSE, eval = FALSE}
rsync -avv --rsh=ssh src/ remote-sys:/dest
```
where `remote-sys` could for example be `user@remote.edu`.


7.   Synchronize between bwunicluster and bwfilestorage
```{r, tidy = FALSE, eval = FALSE}
# 1. Move into the source directory.
cd <source_dir>

# 2. Send the files to the destination directory.
rdata "rsync . $BWFILESTORAGE/<dest_directory/>"### Basic Command
```
